\documentclass[11.5pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[roman]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage[LY1]{fontenc}

% adjust the page margins
\usepackage[scale=0.85]{geometry}

%\usepackage[T1]{fontenc}
%\usepackage{mathpazo}

% personal data
\firstname{Timothy}
\familyname{Andrew}
\title{{\Colorhref[white]{.}{.}}}               % optional, remove the line if not wanted
%\address{street and number}{postcode city}    % optional, remove the line if not wanted
\mobile{+91 9632693686}                    % optional, remove the line if not wanted
%\phone{080 41664170}                      % optional, remove the line if not wanted                          
\email{tim@timothyandrew.net}                      % optional, remove the line if not wanted
\homepage{www.timothyandrew.net}                % optional, remove the line if not wanted
\extrainfo{
					 {\Colorhref[white]{http://twitter.com/timothyandrew }{....................}}{\href{http://twitter.com/timothyandrew}{@timothyandrew}}
					 {\Colorhref[gray]{http://gist.github.com/timothyandrew}{(gist.)}}{\href{http://github.com/timothyandrew}{github.com/timothyandrew}}                                                 
					 {\href {http://in.linkedin.com/in/timothyandrew}{in.linkedin.com/in/timothyandrew}}
					}
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\newcommand\myitem{\item[\textbullet] }
\definecolor{darkgray}{rgb}{0.2,0.2,0.2}
\definecolor{gray}{rgb}{0.6,0.6,0.6}
\newcommand\Colorhref[3][gray]{\href{#2}{\color{#1}#3}}


\begin{document}
\maketitle

\section{Education}
\cventry{2008-2012}{B.E., Computer Science}{CMR Institute of Technology}{Bangalore}{}{}  % arguments 3 to 6 can be left empty
\cventry{2006-2008}{Pre-University}{Christ Junior College}{Bangalore}{}{}

\section{Experience}
\subsection{Professional}
\cventry{2010-2011}{Software Engineering Intern}{SuccessFactors Inc.}{Bangalore}{}{
\begin{itemize}\setlength\itemindent{6pt}
		\myitem Helped rewrite a \textit{Report Builder} Flex app to HTML/Javascript.
		\myitem Wrote Javascript code in JUIC, an in-house framework.
		\myitem Created usable, cross-browser compatible UIs (most clients used IE6).
		\myitem Reworked a number of design decisions with the UX team.
\end{itemize}}
\subsection{Miscellaneous}
\cventry{2011}{Of Rusty Nails and Wounded Hearts}{IMC}{Bangalore}{}{A theater production by the young people of the Indiranagar Methodist Church.
\begin{itemize}\setlength\itemindent{6pt}
		\myitem Designed the media for the play, including posters, banner ads, tickets and a website.
		\myitem Ran a social media campaign targeting Facebook and Twitter.
		\myitem Helped managing live sound, including a soundtrack and some sound effects.
		\myitem Designed and typeset a souvenir given to all attendees.
\end{itemize}}


\section{Skills}
\subsection{Good Working Knowledge}
\cvcomputer{Programming}{C, Java, Ruby}{Web}{HTML, CSS, Javascript}
\cvcomputer{OS}{OS X, Linux, Windows}{SCM}{Git, Subversion}
\cvcomputer{Misc}{Typography, {\Colorhref[darkgray]{http://xkcd.com/208/}{Regular Expressions}}, UI Design, Bash, Photoshop}{}{}
\subsection{Cursory Knowledge}
\cvcomputer{Programming}{C\#}{Misc}{Python, Android, \LaTeX}
\cvcomputer{Web}{SQL, Ruby on Rails, Sinatra, Backbone, Coffeescript, Node.js, Socket.IO, Memcached, jQuery}{}{}
\subsection{Misc}
\cvcomputer{Other Skills}{Touch typing, Eye for detail, Fast learner}{Editor/IDE}{Vim, Textmate, Eclipse, SL2}

\section{Achievements}
\cventry{2011}{Runners-Up at National Finals}{Infosys Aspirations 2020}{}{}{
Aspirations2020 is a platform for students of colleges to prepare themselves to become Global Professionals. Programming Contest under Aspirations2020 encourages the spirit of competitiveness and accelerates learning through extra-curricular activities within the student community.
\newline
\begin{itemize}\setlength\itemindent{6pt}
		\myitem Was part of a team that won the State finals, and won second place at the National level.
		\myitem Both these events took place at the Infosys campus at Electronics City, Bangalore.
\end{itemize}}

\section{Leisure and Hobbies}
\cvline{Music}{\small Bass Guitar (worship band), Acoustic Guitar, Choir singing. Studied Piano for 8 years.}
\cvline{Misc}{\small Play snooker, table tennis and fooseball. F1 Fan. I enjoy a good steak!}
\end{document}
